### 2021-02-24 SupplementaryMaterial/Acknowledgments.tex
update

% Place acknowledgments below.
First of all, I would like to thank my advisor Prof. Dinghao Wu for the continuous support of my Ph.D. study. I had a very hard time during the pandemic. Without his encouragement and support, I could not have finished the program. I also thank Dinghao for inviting me to Switzerland during his sabbatical leave. A large portion of the research presented in the dissertation was finished when I worked in Switzerland. The knowledge and skills I learned from him will also help me make progress in my future career.

Beside my advisor, I would like to thank my committee members, Prof. Peng Liu, Prof. Sencun Zhu, Prof. Benjamin Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.

I would also like to thank Dr. Kang Li, Mr. Zhaofeng Chen, Dr. Mingshen Sun, Dr. Greg Zaverucha and Dr. Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research Lab.  I also thank my friends and collaborators at Penn State University and EPFL.

>>>>

% Place acknowledgments below.
First of all, I would like to thank my advisor Dr. Dinghao Wu for the continuous support of my Ph.D. study. I had a very hard time during the pandemic. Without his encouragement and support, I could not have finished the program. I also thank Dinghao for inviting me to Switzerland on his sabbatical. A large portion of the research presented in the dissertation was finished when I worked in Switzerland. The knowledge and skills I learned from him will also help me make progress in my future career.

Beside my advisor, I would like to thank my committee members, Dr. Peng Liu, Dr. Sencun Zhu, Dr. Benjamin V. Hanrahan, and Prof. James R. Larus for their time, reviewing my dissertation.

I would also like to thank Dr. Kang Li, Mr. Zhaofeng Chen, Dr. Mingshen Sun, Dr. Greg Zaverucha, Dr. Kevin Kane, and Dr. Brian LaMacchia for their help during my internship at Baidu X-Lab and Microsoft Research Lab.  I also thank my friends and collaborators at Penn State University and EPFL.
